---
title: "Matias Leandro Andina's CV"
author: Matias Leandro Andina
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "data/",  
  pdf_mode = params$pdf_mode
)

# filter data !
CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

<!-- Swap image with your preferred logo -->

<!-- ![logo](){width=100%} -->

```{r photo}
source("parse_twitter_pic.r")
im <- parse_twitter_pic()
im
```

##  {#contact}

```{r}
CV %>% print_contact_info()
```

```{r, eval=FALSE}
# Not really interested in this
# also, when rendered, it's not centered

if(params$pdf_mode){
  cat("View this CV online with links at _nickstrayer.me/datadrivencv/_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf)")
}
```

## <i class="fas fa-language"></i> Languages {#languages}

-   Spanish (native)
-   English (bilingual)
-   Portuguese (intermediate)

## <i class="fa fa-code"></i> Programming {#skills}

-   R
-   Python
-   Matlab
-   git / GitHub

## <i class="fa fa-area-chart"></i> Data analysis {#skills}

-   Data visualization (ggplot2, seaborn)
-   Linear models (GLM, GLMM)
-   Machine Learning (sklearn)
-   Image Processing (opencv)

## <i class="fas fa-book-open"></i> Literate Coding {#skills}

-   Quarto
-   Rmarkdown
-   LaTeX

# Main

## Matias Leandro Andina {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Research Experience {data-icon="flask"}

```{r}
CV %<>% print_section('research_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->

<br> <br> 
<br> <br> 
<br> <br>
<br> <br>
<br> <br>

## Teaching Experience {data-icon="chalkboard-teacher"}

::: aside
```{r}
#CV %<>% print_text_block('teaching_experience_aside')
```
:::

```{r}
CV %<>% print_section('teaching_positions')
```

## Selected Publications {data-icon="file"}

```{r}
CV %<>% print_section('academic_articles')
```

Complete publication list at [Google Scholar](https://scholar.google.com/citations?user=PnTVdPAAAAAJ&hl=en).

## Selected Talks & Invited Lectures {data-icon="bullhorn"}

```{r}
CV %<>% print_section('talks')

```

## Conferences
```{r}
CV %<>% print_section('conferences')
```


## Awards {data-icon="star-o"}

```{r}
CV %<>% print_section('awards')
```

## Mentoring {data-icon="handshake-o" data-concise="true"}

```{r}
CV %<>% print_section('mentoring')


```

## Service {data-icon="university"}

```{r}
CV %<>% print_section('service')
```


## Software Development {data-icon="desktop"}

:::aside
I have a strong commitment towards using and developing open source tools. 
:::

```{r}
CV %<>% print_section('software')
```


Complete List of Software at [Github](https://github.com/matiasandina).


## Selected Data Science Writing {data-icon="chart-line"}

::: aside
```{r}
CV %<>% print_text_block('data_science_writing_aside')
```
:::

```{r}
CV %<>% print_section('data_science_writings')
```

```{r}
#CV %<>% print_links()
```

:::footer
Last updated on `r Sys.Date()`.
:::