---
title: "Matias Leandro Andina's CV"
author: Matias Leandro Andina
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
  show_aside:
    value: false
  include_sections: [
    "education",
    "skills", 
    "academic_articles", 
    "teaching_positions", 
    "software",
    "awards", 
    "mentoring"] # toggle on-off interactively or run with params from outside. Order here is not order in CV
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "data/",  
  pdf_mode = params$pdf_mode
)

# filter data !
CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```


```{r setup_sections, include=FALSE}
# All section IDs used in your CV — long and short
all_sections <- c(
  "education",
  "research_positions",
  "academic_articles",
  "teaching_positions",
  "conferences",
  "awards",
  "mentoring",
  "talks",
  "service",
  "software",
  "data_science_writings",
  "skills"
)

# For each section, compute whether to include it and store in a named list
include <- lapply(all_sections, function(sec) {
  sec %in% params$include_sections
})
names(include) <- all_sections
```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```



# Aside

```{r, results='asis'}
if (params$show_aside) {
  cat(knitr::knit_child('sidebar.Rmd', quiet = TRUE))
} else {
  cat("
<style>
  .aside {
    display: none !important;
    width: 2 !important;
    padding: 0 !important;
    margin: 0 !important;
    background: none !important;
  }

  :root {
    --sidebar-width: 2px !important;
    --content-width: 90% !important;       /* expand main content */
    --decorator-width: 0px !important;      /* optional: shifts the timeline spine */
  }

  /* In pagedown templates Content is often placed inside .main / .content */
  .main, .content {
    max-width: 100% !important; 
    width: 100% !important;
  }

</style>
")
}
```

# Main

## Matias Leandro Andina {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```


```{r, eval=include[["research_positions"]]}
knitr::asis_output('## Research Experience {data-icon="flask"}')
```


```{r, eval=include[["research_positions"]]}
if ("research_positions" %in% params$include_sections) {
  CV %<>% print_section('research_positions')
}
```

<!-- These breaks just force a new page so section doesnt get cut off -->

<!--
<br> <br> 
<br> <br> 
<br> <br>
<br> <br>
<br> <br>
 -->


```{r, eval=include[["skills"]]}
knitr::asis_output('## Skills {data-icon="tools" data-concise="true"}')
```

```{r, eval=include[["skills"]]}
CV %<>% print_section('skills')
```

 
## Selected Publications {data-icon="file"}

```{r}
CV %<>% print_section('academic_articles')
```

Complete publication list at <i class="fa fa-link" aria-hidden="true"></i> [Google Scholar](https://scholar.google.com/citations?user=PnTVdPAAAAAJ&hl=en).


## Teaching Experience {data-icon="chalkboard-teacher"}

```{r}
# TODO: Properly parametrize each section
if (params$show_aside) {
  CV %<>% print_section('teaching_positions')
} else {
  CV %<>% print_section("teaching_positions_short")
}
```


## Selected Conferences
```{r}
if (params$show_aside) {
  CV %<>% print_section('conferences')
} else {
  CV %<>% print_section('conferences_short')
}
  
```

Complete conference list in <i class="fa fa-link" aria-hidden="true"></i> [this archive](https://matiasandina.github.io/cv_academic#conferences).


## Selected Awards {data-icon="star-o"}

```{r}
# TODO: Properly parametrize each section
if (params$show_aside) {
  CV %<>% print_section('awards')
}else{
  CV %<>% print_section('awards_short')
}
```

Complete award list in <i class="fa fa-link" aria-hidden="true"></i> [this archive](https://matiasandina.github.io/cv_academic.html#awards).

## Mentoring {data-icon="handshake-o" data-concise="true"}

```{r}
# TODO: Properly parametrize each section
if (params$show_aside) {
  CV %<>% print_section('mentoring')
}else{
  CV %<>% print_section('mentoring_short')
}

```

## Selected Talks & Invited Lectures {data-icon="bullhorn"}

```{r}
CV %<>% print_section('talks')

```


```{r, eval=include[["service"]]}
knitr::asis_output('## Service {data-icon="university"}')
```


```{r, eval=include[["service"]]}
CV %<>% print_section('service')
```



```{r, eval=include[["software"]]}
knitr::asis_output('## Software Development {data-icon="desktop"}')
```


:::aside
I have a strong commitment towards using and developing open source tools. 
:::

```{r, eval=include[["software"]]}
CV %<>% print_section('software')
```


Complete List of Software at [Github](https://github.com/matiasandina).


```{r, eval=include[['data_science_writings']]}
knitr::asis_output('## Selected Data Science Writing {data-icon="chart-line"}')
```


::: aside
```{r, eval=include[['data_science_writings']]}
CV %<>% print_text_block('data_science_writing_aside')
```
:::

```{r, eval=include[['data_science_writings']]}
if (params$show_aside) {
  CV %<>% print_section('data_science_writings')
}else{
  CV %<>% print_section('data_science_writings_short')
}
```

```{r}
#CV %<>% print_links()
```

:::footer
Last updated on `r Sys.Date()`.
:::